Experiment 1 of 4

### 2016-09-14 experiments/e1/writeup/e1.Rmd
renamed the springer chapter template for easier bash-completion
e1 stuff

In this experiment it was possible to identify errors, so error trials were removed. This is because there were only 2 squares and an istruction uniquely identified one of them.

@@

```{r manipulateDataFrame, echo=FALSE}
system("cat ../experimentCode/output/*.dat > ../data/data.txt", wait=TRUE)
dat <- read.delim("../data/data.txt", header=FALSE)
names(dat) <- c("condition", "leftN", "rightN", "vgn", "side", "string", "subject", "rt", "error")
dat$subject <- as.factor(paste("sub",sep="",sprintf("%02d",dat$subject,sep="")))
dat$error <- 1-dat$error
dat$Ord <- ifelse(dat$leftN < dat$rightN, 'LtoR', 'RtoL')
dat$c_Ord <- ifelse(dat$Ord=='LtoR', -.5, .5)
dat$bigside <- ifelse(dat$leftN > dat$rightN, 'L', 'R')
dat$Qty <- ifelse(dat$side==dat$bigside, "Large", "Small")
dat$bigside=NULL
dat$c_Qty <- ifelse(dat$Qty=='Small', -.5, .5)
dat$gap <- as.character(paste("gap", sep=" ", sprintf("%02d",abs(dat$leftN-dat$rightN))))
dat$vgn <- as.factor(ifelse(dat$vgn=="P", "Crisp", "Vague"))
dat$c_Vgn <- ifelse(dat$vgn=='Crisp', -.5, .5)
dat$logrt <- log(dat$rt)
# item_ratio
# NOT DONE YET
write.table(x=dat, "all_trials.txt")
dat$subject <- as.factor(dat$subject)
dat$vgn <- ifelse(dat$vgn=='Crisp', -.5, .5)
dat$gap[dat$gap=="gap 05"] <- -1.5
dat$gap[dat$gap=="gap 10"] <- -.5
dat$gap[dat$gap=="gap 15"] <- .5
dat$gap[dat$gap=="gap 20"] <- 1.5
dat$gap <- as.numeric(dat$gap)
# Separate off correct trials
alltrials <- dat
correct <- subset(dat, error==0)
errors <-  subset(dat, error==1)
```

@@

>>>>

In this experiment it was possible to identify errors, so error trials were removed. This is because there were only 2 squares and an instruction uniquely identified one of them.

@@

```{r manipulateDataFrame, echo=FALSE}
system("cat ../experimentCode/output/*.dat > ../data/data.txt", wait=TRUE)
dat <- read.delim("../data/data.txt", header=FALSE)
names(dat) <- c("condition", "leftN", "rightN", "vgn", "side", "string", "subject", "rt", "error")
dat$subject <- as.factor(paste("sub",sep="",sprintf("%02d",dat$subject,sep="")))
dat$error <- 1-dat$error
dat$Ord <- ifelse(dat$leftN < dat$rightN, 'LtoR', 'RtoL')
dat$c_Ord <- ifelse(dat$Ord=='LtoR', -.5, .5)
dat$bigside <- ifelse(dat$leftN > dat$rightN, 'L', 'R')
dat$Qty <- ifelse(dat$side==dat$bigside, "Large", "Small")
dat$bigside=NULL
dat$c_Qty <- ifelse(dat$Qty=='Small', -.5, .5)
dat$gap <- as.character(paste("gap", sep=" ", sprintf("%02d",abs(dat$leftN-dat$rightN))))
dat$vgn <- as.factor(ifelse(dat$vgn=="P", "Crisp", "Vague"))
dat$c_Vgn <- ifelse(dat$vgn=='Crisp', -.5, .5)
dat$logrt <- log(dat$rt)
# item_ratio
for (c in unique(dat$condition)) {
  x=subset(dat, condition==c)
  x$item_ratio=unique(min(x$leftN,x$rightN)/max(x$leftN,x$rightN))
  dat[dat$condition==c, 'item_ratio']=x$item_ratio
}
write.table(x=dat, "all_trials.txt")
dat$subject <- as.factor(dat$subject)
dat$vgn <- ifelse(dat$vgn=='Crisp', -.5, .5)
dat$gap[dat$gap=="gap 05"] <- -1.5
dat$gap[dat$gap=="gap 10"] <- -.5
dat$gap[dat$gap=="gap 15"] <- .5
dat$gap[dat$gap=="gap 20"] <- 1.5
dat$gap <- as.numeric(dat$gap)
# Separate off correct trials
alltrials <- dat
correct <- subset(dat, error==0)
errors <-  subset(dat, error==1)
```

@@

```{r plotMeansBothV2, fig.width=10, fig.height=4, message=FALSE}
rts <- summarySEwithin(correct, measurevar="logrt", withinvars=c("vgn","item_ratio"))
err <- summarySEwithin(alltrials, measurevar="error", withinvars=c("vgn","item_ratio"))
dodge=0

plot1 =
  ggplot(rts, aes(y=logrt_norm, x=1-as.numeric(abbreviate(item_ratio)), group=vgn, fill=vgn, shape=vgn, ymin=logrt_norm-ci, ymax=logrt_norm+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.01, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=3, position=position_dodge(dodge)) +
  ggtitle("Response time") + 
  ylab("log RT") + 
  xlab("item_ratio Size") +
  scale_x_continuous(breaks = 1-as.numeric(abbreviate(sort(unique(dat$item_ratio))))) +
  scale_fill_grey(name=element_blank(), start=0,end=1)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() ) +
  theme(aspect.ratio=1)+xlab("")

plot2 = 
  ggplot(err, aes(y=error_norm, x=1-as.numeric(abbreviate(item_ratio)), group=vgn, fill=vgn, shape=vgn, ymin=error_norm-ci, ymax=error_norm+ci)) + 
  geom_line(position=position_dodge(dodge)) + 
  geom_errorbar(width=.01, lty=1, position=position_dodge(dodge)) + 
  geom_point(pch=21, size=3, position=position_dodge(dodge)) +
  ggtitle("Error rate") + 
  ylab("error rate") + 
  xlab("item_ratio Size") +
  scale_x_continuous(breaks = 1-as.numeric(abbreviate(sort(unique(dat$item_ratio))))) +
  scale_fill_grey(name=element_blank(), start=0,end=1)+
  theme_bw()+
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.key = element_blank() )+
  theme(aspect.ratio=1)+xlab("")
